Nail: A practical interface generator for binary formats

### 2014-04-01 paper/intro.tex
merged changes

Finally, many protocol implementations are so complicated that even without bugs, they inadvertently
provide a full Turing-complete execution environment. Examples include X86 page tables
\cite{bangert2013page}, ELF symbols and relocations\cite{shapiro2013weird}.  
The more powerful an input
protocol is, the more control an attacker gains over a systems state - and power to manipulate a
systems state is also a degree of undeserved trust. In the offensive research community, this has
been generalised into treating a program as a \textit{weird machine}\cite{bratus2011exploit} that
operates on an input, analogous to a virtual machine operating on bytecode.

Proper input recognition has been shown to be an excellent way of eliminating malicious inputs. In
one case, a hand-written PDF parser could eliminate $98\%$ of known malicious PDFs\cite{Bogk-PDF}.

>>>>

Finally, many protocol implementations are so complicated that even without bugs, they inadvertently
provide a full Turing-complete execution environment. Examples include X86 page tables
\cite{bangert2013page}, ELF symbols and relocations\cite{shapiro2013weird}. Even though these
protocols were never intended to be that expressive - and consequentially hard to parse, implementation details of their
recognisers - which de facto became a part of the specification and were relied upon by legitimate
inputs - expose unwanted computational power and have unintended side-effects.
In the offensive research community, this has
been generalised into treating a program as a \textit{weird machine}\cite{bratus2011exploit} that
operates on an input, analogous to a virtual machine operating on bytecode.

Proper input recognition has been shown to be an excellent way of eliminating malicious inputs. In
one case, a  PDF parser implemented in Coq could eliminate over $95\%$ of known malicious PDFs\cite{Bogk-PDF}.
However, manually writing parser code does not scale to the number of file formats  and protocols in
existence and might result in parser code tied to one specific application.
